---
title: "Suffolk County Council"
date: "`r Sys.Date()`"
scctemplate:
  header:
    site_branding: "Suffolk County Council"
  navigation:
    breadcrumb_trail:
      - href: "index.html"
        text: "Home"
      - text: "Suffolk County Council"
    toc:
      sticky: false
      numbered: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(dplyr)
library(leaflet)
```

# Find your councillor

Use the map below to find your Councillor. Hover over each electoral district to see the name of the district. 

Click on the district to get more information about the Councillor. You can also search by location using the search icon on the left.

Clicking on a Councillor's name will take you to their profile on the Suffolk County Council [Find Your Councillor website](https://www.suffolk.gov.uk/council-and-democracy/councillors-and-elected-representatives/find-your-councillor).

```{r map, echo = FALSE, warning = FALSE, message = FALSE, out.width = "100%", fig.align='center'}
library(httr)
library(XML)
library(dplyr)
library(rvest)
library(leaflet)
library(here)
library(sf)
library(dplyr)
library(tidyr)
library(mapview)
library(leafem)
library(leaflet.extras)
library(htmlwidgets)
library(htmltools)

# simple <- read_html("https://www.suffolk.gov.uk/council-and-democracy/councillors-and-elected-representatives/find-your-councillor")
councillors <- readr::read_csv("opencouncildata_councillors.csv") |> 
  dplyr::filter(council == "Suffolk") |> 
  janitor::clean_names()

ced <- st_read("L:\\MAPINFO\\DATA\\data_new\\BoundaryLine\\OS_2021_DATA\\Data\\GB\\county_electoral_division.tab", quiet = TRUE) |> 
  dplyr::filter(File_Name == "SUFFOLK_COUNTY")

ced <- st_transform(ced, 4326)

ced$Name <- gsub(" ED", "", ced$Name)
ced$Name <- gsub("St\\.", "St", ced$Name)

ced <- left_join(ced, councillors, by = c("Name" = "ward_name"))

ced <- ced |> 
  select(Name, councillor_name, party_name)

ced$councillor_name <- gsub(" MBE DL", "", ced$councillor_name)

ced$councillor_lower <- tolower(ced$councillor_name)
ced$councillor_lower <- gsub(" ", "-", ced$councillor_lower)

ced$image <- paste0("https://www.suffolk.gov.uk/image-library/", ced$councillor_lower, "-ws-hr.jpg")

ced$html <- paste0("https://www.suffolk.gov.uk/council-and-democracy/councillors-and-elected-representatives/find-your-councillor/", ced$councillor_lower)

colours <- data.frame(
  party_name = c(
    "Green Party",
    "Conservative and Unionist",
    "Labour Party",
    "Liberal Democrats",
    "Independent / Other",
    "West Suffolk Independents"
  ),
  hex = c(
    "#6DC23B",
    "#00AEEF",
    "#E4003B",
    "#FAA01A",
    "#B1B4B6",
    "#A395A5"
  )
)

ced <- left_join(ced, colours, by = c("party_name" = "party_name"))

test <- lapply(unique(ced$Name), function(district) {
  counts <- ced |> 
    dplyr::filter(Name == district) |> 
    select(-councillor_lower)
  
    counts$count <- 1
  
  if(nrow(counts) > 1 ) {
    counts <- counts %>%
      summarise_all(str_c, collapse = ', ')
    
    counts$count <- 2
  }
  return(counts)
})

lapply(ced$councillor_name, function(x) {
  str_detect(x, "\\,")
})

ced <- bind_rows(test)
ced$Name <- gsub("(.*),.*", "\\1", ced$Name)
ced$count <- gsub("(.*),.*", "\\1", ced$count)

ced2 <- ced |> 
  filter(count == 2)

ced <- ced |> 
  filter(count == 1)

division_popup <- sprintf(
  "<strong>%s</strong><br/><strong><a href = %s>%s</a></strong><br/><strong><span style='color:%s;'>%s</span></strong><br/><img src=%s width = 240px/>",
  ced$Name, ced$html, ced$councillor_name, ced$hex, ced$party_name, ced$image
) %>% lapply(htmltools::HTML)

seperated <- separate(
  ced2,
  html,
  into = c("html1", "html2"),
  sep = ","
)

seperated <- separate(
  seperated,
  councillor_name,
  into = c("councillor_name1", "councillor_name2"),
  sep = ","
)

seperated <- separate(
  seperated,
  image,
  into = c("image1", "image2"),
  sep = ","
)

seperated <- separate(
  seperated,
  party_name,
  into = c("party_name1", "party_name2"),
  sep = ","
)

seperated <- separate(
  seperated,
  hex,
  into = c("hex1", "hex2"),
  sep = ","
)

division_popup2 <- sprintf(
  "<strong>%s</strong><br/><strong><a href = %s>%s</a></strong><br/><strong><span style='color:%s;'>%s</span></strong><br/><img src=%s width = 240px/><br/><strong><a href = %s>%s</a></strong><br/><strong><span style='color:%s;'>%s</span></strong><br/><img src=%s width = 240px/>",
  seperated$Name, seperated$html1, seperated$councillor_name1, seperated$hex1, seperated$party_name1, seperated$image1, seperated$html2, seperated$councillor_name2, seperated$hex2, seperated$party_name2, seperated$image2
) %>% lapply(htmltools::HTML)

division_popup <- append(division_popup, division_popup2)

ced <- bind_rows(ced, ced2)

division_label <- sprintf(
  "<strong>%s</strong><br/>Click for more information",
  ced$Name
) %>% lapply(htmltools::HTML)

ced$hex <- gsub("#6DC23B, #6DC23B", "#6DC23B", ced$hex)
ced$hex <- gsub("#00AEEF, #00AEEF", "#00AEEF", ced$hex)

councillor_map <- leaflet() |> 
  addTiles(group = "Topo") |> 
  addPolygons(
    data = ced,
    group = "County Electoral Division",
    color = "black",
    opacity = 1,
    weight = 2,
    fillColor = ced$hex,
    fillOpacity = 0.2,
    highlightOptions = highlightOptions(
      color = "white",
      weight = 4,
      fill = "#666",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = division_label,
    labelOptions = labelOptions(
      style = list("font-weigth" = "normal", padding = "3px 8px"),
      textsize = "20px",
      direction = "auto"
    ),
    popup = division_popup,
    popupOptions = popupOptions(
      style = list("font-weigth" = "normal", padding = "3px 8px"),
      textsize = "20px",
      direction = "auto"
    )
  ) |> 
  addLayersControl(
    data = ced,
    overlayGroups = c(
      "County Electoral Division"
    ),
    position = "bottomright"
  ) |> 
  addSearchFeatures(
    targetGroups = c("County Electoral Division", ced$councillor_name),
    options = searchFeaturesOptions(
      hideMarkerOnCollapse = TRUE,
      zoom = 12
    )) |> 
  addFullscreenControl()

councillor_map
```
